Of judges, aliens and total preorders

### 2021-02-02 paper/1901_3230880_philip_heltweg.tex
feat: removed l conditionalisation reference, added info about admissible revision

% TODO: discussed in \cite{Katsuno1991} correct? was mentioned in intro of Admissible and Restrained Revision
A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (tpos) \cite{Booth2011}, discussed in \cite{Katsuno1991}. In "How to Revise a Total Preorder", Booth and Meyer describe how to model the change of these total preorders when new evidence becomes available. Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps. It therefore places the article in the field of iterated belief revision.

@@

The next group of properties, \ref{AST3}-\ref{AST5} are common rules in iterated belief change. Booth and Meyer themselves consider them characteristic for admissible revision operators \cite{Booth2006a}.
If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}). These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in section \ref{chapter:dp-agm-postulates}.
In a similar way \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}. It means the following: A world $x$ that is considered at least as plausible as a world $y$ before a revision by new information $\alpha$. If $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$) then after revision $x$ should be considered strictly more plausible than $y$. This rule was not only proposed by Booth and Meyer \cite{Booth2006a} but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).

% TODO: WHAT ARE ADMISSIBLE OPERATORS
%info here: \cite{Booth2006a}
% see also http://ceur-ws.org/Vol-2445/paper_2.pdf
% see also: Whiwap: Checking Iterative Belief Changes

@@

% TODO: probably don't need geffner ref here
Booth and Meyer propose an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$ (also known as L-conditionalisation in Spohn-type rankings \cite{Geffner1992}). Other operators are possible and an area of further research \cite{Booth2011}. They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$ to:

>>>>

A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (tpos) \cite{Booth2011}, also discussed in \cite{Katsuno1991}. In "How to Revise a Total Preorder", Booth and Meyer describe how to model the change of these total preorders when new evidence becomes available. Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps. It therefore places the article in the field of iterated belief revision.

@@

The next group of properties, \ref{AST3}-\ref{AST5} are common rules in iterated belief change. Booth and Meyer themselves consider them characteristic for admissible revision operators, a class of operators that requires new evidence to not be ignored completely \cite{Booth2006a}. This is in contrast to revision strategies like natural revision by Boutilier \cite{Boutilier1996} that minimise change in conditional beliefs.
If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}). These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in section \ref{chapter:dp-agm-postulates}.
In a similar way \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}. It means the following: A world $x$ that is considered at least as plausible as a world $y$ before a revision by new information $\alpha$. If $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$) then after revision $x$ should be considered strictly more plausible than $y$. This rule was not only proposed by Booth and Meyer \cite{Booth2006a} but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).

@@

Booth and Meyer propose an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$. Other operators are possible and an area of further research \cite{Booth2011}. They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$ to:
